What Is React Native ?

React Native is a JavaScript framework for writing real, 
natively rendering mobile applications for iOS and Android. 
It’s based on React, Facebook’s JavaScript library for building user 
interfaces, but instead of targeting the browser, it targets mobile platforms. 
In other words: web developers can now write mobile applications that look and 
feel truly “native,” all from the comfort of a JavaScript library that we 
already know and love. Plus, because most of the code you write can be shared 
between platforms, React Native makes it easy to simultaneously develop for 
both Android and iOS.

Similar to React for the Web, React Native applications are written using 
a mixture of JavaScript and XML-esque markup, known as JSX. Then, under the 
hood, the React Native “bridge” invokes the native rendering APIs in 
Objective-C (for iOS) or Java (for Android). Thus, your application will 
render using real mobile UI components, not webviews, and will look and feel 
like any other mobile application. React Native also exposes JavaScript 
interfaces for platform APIs, so your React Native apps can access platform 
features like the phone camera, or the user’s location.

React Native currently supports both iOS and Android, and has the potential 
to expand to future platforms as well. In this book, we’ll cover both iOS and 
Android. The vast majority of the code we write will be cross-platform. 
And yes: you can really use React Native to build production-ready mobile 
applications! Some anecdota: Facebook, Palantir, and TaskRabbit are already 
using it in production for user-facing applications.