How to install NPM and How to check version of NPM ?

How to Check NPM Version?

Enter “cmd” to open the Command Prompt.
NPM -- version or NPM -v 

What is NPM?

NPM is an abbreviation for “Node Package Manager,” which is the default 
package manager for JavaScript's runtime Node.js. One of the largest 
software registries, NPM installs the packages and provides a user interface 
to work interactively. 
It works as both a command-line interface (CLI) tool as well as a repository. 
Using it as a repository helps developers release and share reusable code and 
is composed of 800,000 packages. Whereas using it as a CLI tool allows users to 
download and install packages for the applications.

The following four lines describe NPM the best:

Currently, it is the largest and most used software registry in the world.
NPM contains more than 800,000 code packages for users.
Open-source developers also use NPM to share software.
Many businesses and organizations use NPM for better management of private development.


How to Install NPM?
The installation process of NPM is straightforward and done with the 
installer package available at the Node.js website. However, an individual 
must be well-versed with the applications to issue command-line instructions, 
such as Windows Command Prompt and Git shell.

How to Install NPM on Windows or macOS
Visit the page Nodejs.org and download the package installer.
Run the installer downloaded in the step above.
Follow the instructions given in the installer, like accepting the license agreement, 
clicking on “next,” and accepting the default installation.
Restart the computer to run NPM successfully. 