What is JSX?

JSX stands for JavaScript syntax extension. It is a JavaScript extension that allows us to 
describe React's object tree using a syntax that resembles that of an HTML template. 
It is just an XML-like extension that allows us to write 
JavaScript that looks like markup and have it returned from a component.

JSX stands for Javascript XML and it is a very useful tool for React developers. 
JSX is an extension of the JavaScript language which provides a way to structure 
component rendering using syntax similar to HTML. JSX gives us the ability to write 
HTML elements in Javascript and place them in the DOM by converting the HTML tags 
into React elements without the need for other methods like createElement() or appendChild(). 
This combination of Javascript and HTML leads to having more powerful 
applications with boosted performance.

React is aware of and embraces the fact that UI logic is coupled with rendering logic 
when referring to things such as how the state changes over time, how the data is displayed 
and how events are handled. What makes React unique and powerful is the fact that they 
utilize something called separating “concerns” by coupling units inside components that 
contain both markup and logic, rather than putting them in separate files.

Another popular use case with JSX is its ability to provide a range of element 
attributes designed to mirror those provided by HTML. Custom attributes can be passed 
to the component and all attributes will be received by the component as props.