What are the differences between a class component and functional component ?

1)
Functional Components : A functional component is just a plain JavaScript 
                        pure function that accepts props as an argument and 
                        returns a React element(JSX).

Class Components : A class component requires you to extend from React. 
                   Component and create a render function that returns a React element.

2)
Functional Components : There is no render method used in functional components.

Class Components : It must have the render() method returning JSX 
                   (which is syntactically similar to HTML)

3)
Functional Components : Functional component run from top to bottom and 
                        once the function is returned it can’t be kept alive.

Class Components : The class component is instantiated and different life cycle 
                   method is kept alive and is run and invoked depending on the 
                   phase of the class component.

4)
Functional Components : Also known as Stateless components as they simply 
                        accept data and display them in some form, 
                        they are mainly responsible for rendering UI.

Class Components : Also known as Stateful components because they 
                   implement logic and state

5)
Functional Components : React lifecycle methods (for example, componentDidMount) 
                        cannot be used in functional components

Class Components : React lifecycle methods can be used inside 
                   class components (for example, componentDidMount)

6)
Functional Components : Hooks can be easily used in functional 
                        components to make them Stateful.
                        example: const [name,SetName]= React.useState(‘ ‘)
                       

Class Components : It requires different syntax inside a class component to implement hooks.   
                   example: constructor(props) {
                         super(props);
                         this.state = {name: ‘ ‘}
                   }
                

7)
Functional Components : Constructors are not used.

Class Components : 	Constructor is used as it needs to store state

8)
Functional Components :  example: const Car=()=> {
                                       return <h2>Hi, I am also a Car!</h2>;
                                  }

Class Components : example: class Car extends React.Component {
                                    render() {
                                       return <h2>Hi, I am a Car!</h2>;
                                    }
                            }