What is State?

The status of a react class component instance can be described as an 
object of a collection of observed features that control the component’s 
behavior. In other words, the component’s state is an entity with some 
details that can alter during the component’s lifetime.

This data is kept inside a component. This particular aspect is local or owned. 
The component itself uses the setStatus function to update the state. 

The state is an updated structure that is used to contain and can 
modify data or information about the component over time. 
The state change may occur as a user activity or device event response. 
It decides the actions of the component and how it is to be done by the core 
of the React component. 

As easy as possible, a state should be held. It is the local state or 
details of the part. Only in the component or by the component directly 
can it be accessed or changed. 

Components of react have a built-in state object. 
The state object is where the property values belonging to the item are stored. 
The component is restored when the state object changes.

----------------------------------------------------------------------------------
What are Props?

React is a library focused on components that separate the user interface 
into reusable little bits. These components have to transmit 
(send data to each other) in some cases, and the way to transmit data among 
components is through props. 

“Props” is a special React keyword for proprietary purposes, 
used for data transmission from component to component. 

But the key part of this is the transmission of data with props in a 
uniform flow. (parent-to-child route)

In addition, props data are read-only, meaning that parent data 
cannot be modified by child elements.

---------------------------------------------------------------------------------
difference between state and props?

1)
State : State is managed within the component

Props : Props gets passed to the component

2)
State : State can be changed(mutable)

Props : Props are read only and cannot be changed (immutable)

3)
State : State can be accessed using the use state hooks in functional 
        components and in-class components can be accessed using this. State

Props : Props can be accessed in functional component using props 
        parameter and in-class component, 
        props can the accessed using this.props

4)
State : State changes can be asynchronous

Props : Props are read only

5)
State : State is controlled by react components

Props : Props are controlled by whoever renders the components

6)
State : State can used to display changes with the component

Props : Props are used to communicate between components